A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
For Camera ready Changes to address Points 3 and 5

\vspace{1ex}
\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions as we do, for C.  Beyond focusing on Java in a larger dataset~\cite{dyer2013}, we also study
replacements, omitted from that analysis.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair, an orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique, and show that doing so results in higher-quality repairs; 
we study their templates heuristically on
a different dataset. Their results motivate
studies of human repairs, as it may result in better patches.
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new technique.  Rather, it serves as a starting
point for research on the repair of Java bugs.

@@

\noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
the replacement likelihood for our dataset 
(each cell shows the percent of the time that the statement in the \emph{row}
was replaced by a statement of the type in the \emph{column}). For example, if
the cell in the DoStatement row (row 5) and AssertStatement column (column 2)
shows 0.81, it means that Do statements were
replaced by Assert statements 0.81\% of the times.

@@

>>>>

\vspace{1ex}
\noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much larger dataset~\cite{dyer2013} with 380,125 repositories, and we also study
replacements, omitted from Zhong and Su's analysis.  Barr et al.~\cite{Barr14fse} studied changes to
Java programs to understand the ``Plastic Surgery Hypothesis'' underlying
certain types of program repair, an orthogonal
concern. Kim et al.~\cite{kim2013} manually analyze 
changes to Java programs to inform an automated repair
technique, and show that doing so results in higher-quality repairs; 
we study their templates heuristically on
a different dataset. Their results motivate
studies of human repairs, as it may result in better patches.
Long and Rinard learn probabilistic models from bug fixes to C
code~\cite{Long2016}. Our analysis is significantly less precise and does not
inform a new technique.  Rather, it serves as a starting
point for research on the repair of Java bugs.

@@

\noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
the replacement likelihood for our dataset 
(each cell shows the percent of the time that the statement in the \emph{row}
was replaced by a statement of the type in the \emph{column}). For example, if
the cell in the Do statement row (row 5) and Assert statement column (column 2)
shows 0.81, it means that Do statements were
replaced by Assert statements 0.81\% of the times.

@@

An important study that works as a great complement for this study is~\cite{martinez2013}, in which they discuss a probability distribution for when to apply which kind of edit, meanwhile we go finer grain and discuss a probability distribution of each statement type, once the program has already chosen a kind of edit. It is also worth mentioning that this paper has studied 14 repositories with 89,993 versioning transactions, while our study studies 380,125 repositories with 23,229,406 revisions.
